A game-theory modeling approach to utility and strength of interactions dynamics in biomedical research social networks

### 2017-03-27 casm.tex
Respuesta a revisor 3, pregunta 3

\subsection*{Network initialization and agent state update}

@@

The probability for an agent to cooperate or defect depends on a
number ($\eta$) that refers to a historical balance between average
utility and the average strength of the connections with its
neighbors. It is modeled so because we assume that whatever the result
in utility or strength of interaction, as long as one of them
increases, the player will be confident in the strategy followed so
far. In every simulation step, each player will play both games with
every neighbor, but set its decision to cooperate or defect beforehand
by assessing the overall situation of its relationships. This may
sound odd, since one may think that a person decides for each
relationship separately. However in this way players are optimizing
access to resources and the strength of interactions to their
neighbors at the same time, since their state is set by
considering both together.\\

>>>>

\subsection*{Model update}

@@

The probability for an agent to cooperate or defect depends on a
number ($\eta$) that refers to a historical balance between average
utility and the average strength of the connections with its
neighbors. It is modeled so because we assume that whatever the result
in utility or strength of interaction, as long as one of them
increases, the player will be confident in the strategy followed so
far. In every simulation step, each agent will independently play both games with
every neighbor. Nonetheless, the agent sets its decision to cooperate or defect beforehand
by assessing the overall situation of its relationships. This may
sound odd, since one may think that a person decides for each
relationship separately. However in this way players are optimizing
access to resources and the strength of interactions to their
neighbors at the same time, since their state is set by
considering both together. The strength of interaction is updated independently for each pair of agents.  In a single play some interactions might be weakened, some may get strengthened and others may remain unaffected. Moreover, in this model, history is kept in the network as strength of interactions and it conditions the agent\'s disposition to cooperate or to defect. As the sayings go: Burnt children dread fire; A bad dog is not born but made.\\
